---
title: "qualtrics_survey"
format: html
editor: visual
---

## Pulling and Displaying Data from a Qualtrics Survey

We have a fake survey about favorite colors and emotions named `Test Survey` in use in my University of Michigan qualtrics account.

```{r setup}
#| echo: true
library(tidyverse)
library(qualtRics)
```

Note that the qualtrics API key is stored in both my local .Renviron file for rendering locally (good for testing), and in a Github Actions repository secret for running as a Github Action. The GHA is directed by a separate `.github/workflows/publish.yml` file on push (when I push changes to the repo to Github) or on a cron schedule that runs once weekly on Sundays to update the website.

Let's use this to read in data from `Test Survey`.

Note that we had to change our qualtrics site base url from <https://umich.qualtrics.com/> because it was being proxied.

This is per issue #339 for the qualtrics package.

<https://github.com/ropensci/qualtRics/issues/339>

Details on using the qualtRics package can be found at <https://cran.r-project.org/web/packages/qualtRics/vignettes/qualtRics.html>.

Set up credentials:

```{r creds}
#| echo: true
qualtrics_api_credentials(api_key = Sys.getenv("QUALTRICS_API_KEY"), 
                          base_url = "yul1.qualtrics.com",
                          overwrite = TRUE)
```

Now we can read in some data on my available surveys.

```{r read-all-surveys}
#| warnings: false
#| messages: false
surveys <- all_surveys()
head(surveys)
```

Now read in some fictional data from one particular `Test Survey`,\
and display a simple table of responses.

```{r read-survey}
my_survey <- fetch_survey(surveyID = 'SV_5omMPxaTCy2m0Ki')
my_survey |> 
  select(Q2:Q4_3) |> 
  purrr::set_names(c('name', 'fav_color', 'anxiety', 'depression', 'happiness')) |> 
  head()
```
