---
title: "qualtrics_survey"
format: html
editor: visual
---

## Qualtrics is a survey platform

We have a survey named `Test Survey` in use.

```{r setup}
library(tidyverse)
library(qualtRics)
```

Note that the qualtrics API key is stored in .Renviron for rendering locally, and in a Github Actions repository secret for running as a Github Action. The GHA is directed by a separate `.github/workflows/publish.yml` file on push or on cron schedule once weekly.

Let's use this to ready in data from `Test Survey`.

Note that we had to change the qualtrics site base url because it was being proxied.

Per issue #339 for the qualtrics package.

<https://github.com/ropensci/qualtRics/issues/339>

Set up credentials:

```{r creds}
#| echo: true
qualtrics_api_credentials(api_key = Sys.getenv("QUALTRICS_API_KEY"), 
                          base_url = "yul1.qualtrics.com",
                          overwrite = TRUE)
```

Now we can read in some data.

```{r read-all-surveys}
surveys <- all_surveys()
head(surveys)
```

Now read in some fictional data from `Test Survey`.

```{r read-survey}
my_survey <- fetch_survey(surveyID = 'SV_5omMPxaTCy2m0Ki')
my_survey |> 
  select(Q2:Q4_3) |> 
  purrr::set_names(c('name', 'fav_color', 'anxiety', 'depression', 'happiness')) |> 
  head()
```
